### 2012-12-26 inst/examples/allee.Rmd
corrected the policy calculation to correspond to f(x-h) rather than f(x) - h

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::notebook.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

@@

```{r}
matrices_same <- gp_transition_matrix(sapply(x_grid, f, 0, p), gp$ZZ.vark, x_grid, h_grid) 
opt_same <- find_dp_optim(matrices_same, x_grid, h_grid, OptTime, xT, profit, delta=delta, reward = reward)
```

>>>>

```{r graphing-options, include=FALSE}
#opts_knit$set(upload.fun = socialR::notebook.url)
#opts_chunk$set(dev = 'Cairo_pdf', dev.args=list(""))
opts_chunk$set(dev="png", dev.args=list(bg="transparent"))
opts_chunk$set(comment=NA, tidy=FALSE)
theme_set(theme_bw(base_size=16))
theme_update(panel.background = element_rect(fill = "transparent",colour = NA),
             plot.background = element_rect(fill = "transparent",colour = NA))
cbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
sha <- gsub("^commit ", "", system("git log -n 1", intern=TRUE)[1])
short_sha <- gsub("(^.{10}).*", "\\1", sha)
date <- format(Sys.time(), "%Y-%m-%d-%H-%M-%S")
opts_chunk$set(fig.path = paste("figure/", date, "-", short_sha, "-", sep=""))

@@

```{r}
matrices_same <- gp_transition_matrix(sapply(x_grid, f, 0, p),rep(sigma_g, length(gp$ZZ.vark)), x_grid, h_grid) 
opt_same <- find_dp_optim(matrices_same, x_grid, h_grid, OptTime, xT, profit, delta=delta, reward = reward)
```
